Using the internal language of toposes in algebraic geometry

### 2016-05-24 slides-cambridge2016.tex
British English spelling

\IfSubStr{\jobname}{\detokenize{nonotes}}{
  \setbeameroption{hide notes}
}{
  \setbeameroption{show notes}
}
\setbeamertemplate{note page}[plain]
%\setbeameroption{hide notes}  % XXX

@@

    A particularly interesting task is to internalize the
    construction of the relative spectrum, which, given a quasicoherent sheaf of algebras
    on a scheme~$X$, yields a scheme over~$X$. From the internal point of
    view, this construction should simply reduce to an intuitionistically sensible
    variant of the ordinary construction of the spectrum of a ring, but it turns
    out that this expectation is too naive and that a refined approach is
    necessary.

@@

    \item There are two further rules concerning the constants~$\top$
    and~$\bot$ (truth resp. falsehood):
      \[ \renewcommand{\arraystretch}{1.3}\begin{array}{@{}lcl@{}}
        U \models \top &\Ll& U = U \text{ (always fulfilled)}\\
        U \models \bot &\Ll& U = \emptyset
      \end{array} \]

@@

\begin{frame}\frametitle{The absolute spectrum, internalized}
  Let~$A$ be a commutative ring in a topos~$\E$.

@@

\begin{frame}\frametitle{Semi-open and open tasks}
  \begin{itemize}
  \item Characterize quasicoherence in the big Zariski topos.
  \item Understand how to work with~${\flat} \dashv \sharp$.
  \item Do cohomology in the little Zariski topos; exploit that higher direct
  images look like ordinary sheaf cohomology from the internal point of view.
  \item Do cohomology in the big Zariski topos.
  \item Understand more subtoposes of the big Zariski topos.
  \item Derive suitable axioms for synthetic algebraic geometry.
  \end{itemize}

@@

@@

* typo fulfil

>>>>

\IfSubStr{\jobname}{\detokenize{nonotes}}{
  \setbeameroption{hide notes}
}{
  \setbeameroption{show notes}
}
\setbeamertemplate{note page}[plain]

@@

    A particularly interesting task is to internalise the
    construction of the relative spectrum, which, given a quasicoherent sheaf of algebras
    on a scheme~$X$, yields a scheme over~$X$. From the internal point of
    view, this construction should simply reduce to an intuitionistically sensible
    variant of the ordinary construction of the spectrum of a ring, but it turns
    out that this expectation is too naive and that a refined approach is
    necessary.

@@

    \item There are two further rules concerning the constants~$\top$
    and~$\bot$ (truth resp. falsehood):
      \[ \renewcommand{\arraystretch}{1.3}\begin{array}{@{}lcl@{}}
        U \models \top &\Ll& U = U \text{ (always fulfiled)}\\
        U \models \bot &\Ll& U = \emptyset
      \end{array} \]

@@

\begin{frame}\frametitle{The absolute spectrum, internalised}
  Let~$A$ be a commutative ring in a topos~$\E$.

@@

\begin{frame}\frametitle{Semi-open and open tasks}
  \begin{itemize}
  \item Characterise quasicoherence in the big Zariski topos.
  \item Understand how to work with~${\flat} \dashv \sharp$.
  \item Do cohomology in the little Zariski topos; exploit that higher direct
  images look like ordinary sheaf cohomology from the internal point of view.
  \item Do cohomology in the big Zariski topos.
  \item Understand more subtoposes of the big Zariski topos.
  \item Derive suitable axioms for synthetic algebraic geometry.
  \end{itemize}

@@

\begin{frame}
  \slogan{\hil{Understand notions and statements of algebraic geometry
  as notions and statements of algebra internal to appropriate toposes.}}

  {\vspace{-0.1em}\centering
  \rotatebox{90}{\tiny\scalebox{0.5}{Illustration: Carina Willbold}}\hspace{-0.05cm}%
  \includegraphics[scale=0.20]{images/external-internal-small}
  \par\medskip\vspace{-0.1em}}

  \begin{itemize}
    \item Simplify proofs and gain conceptual understanding.
    \item Understand relative geometry as absolute geometry.
    \item Develop a synthetic account of scheme theory.
    \item Contribute to constructive algebra.
  \end{itemize}

  \centering
  \hil{\href{http://tiny.cc/topos-notes}{http://tiny.cc/topos-notes}}
  \par
\end{frame}

@@
